### 2018-08-03 abstract.tex

Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced demand in building the tools to analyze these systems. This paper introduces a Python script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt. SaltProc couples with the Monte Carlo code, SERPENT 2, for neutron transport and depletion calculations. SaltProc capabilities was illuminated for full-core depletion in the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could be achieved after 16 years and (2) the multiplication factor stabilizes after 6 years of operation. Fuel salt irradiation with online reprocessing causes considerable neutron energy spectrum hardening; this spectral shift has a problematic impact on safety parameters (e.g., temperature reactivity feedback, reactivity control system worth). Volatile gases and noble metals removal has positive effect on the core performance approximately 7500 pcm over 10-years timeframe; rare earth elements removal has slower rate and less impact on reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 years of operation is 100 g/GWh$_e$ which is a good agreement with other recent research. Problematic effects of neutron energy spectrum hardening during \gls{MSBR} operation should be taken into account for neutronics, multi-physics, and fuel cycle performance analysis.

>>>>

Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced 
demand for tools to analyze these systems. This paper introduces a Python 
script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
changing isotopic composition of an irradiated fuel salt. SaltProc couples with 
the Monte Carlo code, SERPENT 2, for neutron transport and depletion 
calculations. SaltProc capabilities was illuminated for full-core depletion in 
the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could 
be achieved after 16 years and (2) the multiplication factor stabilizes after 6 
years of operation. Fuel salt irradiation with online reprocessing causes 
considerable neutron energy spectrum hardening; this spectral shift has a 
problematic impact on safety parameters (e.g., temperature reactivity feedback, 
reactivity control system worth). Volatile gases and noble metals removal has 
positive effect on the core performance approximately 7500 pcm over 10-years 
timeframe; rare earth elements removal has slower rate and less impact on 
reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 
years of operation is 100 g/GWh$_e$ which is a good agreement with other recent 
research. Problematic effects of neutron energy spectrum hardening during 
\gls{MSBR} operation should be taken into account for neutronics, 
multi-physics, and fuel cycle performance analysis.

### 2018-08-03 methods.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline 
        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
        Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
        \qquad & Eu & 500 days \\ 
        Noble metals & Se, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ 
        Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
        Salt discard & Th, Li, Be, F & 3435 days \\ 
        Protactinium & $^{233}$Pa & 3 days \\ 
        Higher nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only. Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
        \label{tab:reprocessing_list}
\end{table}
Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations. If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition. On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured. To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        %\footnotetext{Chemical processing plant and gas separation system 
        %removing chemical elements (not isotopes) only. Isotopes instead of 
        %elements listed because other isotopes are short-lived and might be 
        %ignored.}
        \label{tab:reprocessing_list}
\end{table}
Th removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, the time interval for depletion calculations in this 
model was selected as 3 days to correlate with the removal interval of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.
